### 2020-06-05 tex/presentation.tex
Add motivation slide.
Make workflow graphs nicer.
Fix graph height.

@@

  \begin{frame}{Outline}
    \begin{itemize}
      \item Introduction
      \item Overview of the Project Workflow
      \item Evaluation of Scraping Tools
      \item Implementation
      \begin{itemize}
        \item Scraping
        \item Natural Language Processing
        \item Data Analysis
      \end{itemize}
      \item Findings
      \item Conclusion
    \end{itemize}
  \end{frame}

  \begin{frame}{Introduction}
    \begin{itemize}
      \item information security becoming an essential area of expertise
      \item same understanding of the required skills by both companies and prospective employees
      \item scraping of three popular job search websites: Monster, Indeed and StepStone
      \item analysis of scraped data
    \end{itemize}
  \end{frame}

  \begin{frame}{Overview of the Project Workflow}
    \includegraphics[width=\textwidth]{project-workflow.dot.pdf}
  \end{frame}

@@

  \begin{frame}{Findings: Employment Type}
    \includegraphics[width=\textwidth]{employment-type-bar-chart.pdf}
  \end{frame}

  \begin{frame}{Findings: Education Type}
    \includegraphics[width=\textwidth]{education-bar-chart.pdf}
  \end{frame}

  \begin{frame}{Findings: Location}
    \includegraphics[width=\textwidth]{location-bar-chart.pdf}
  \end{frame}

  \begin{frame}{Findings: Location per Capita}
    \includegraphics[width=\textwidth]{location-per-capita-bar-chart.pdf}
  \end{frame}

  \begin{frame}{Findings: Average Salary}
    \includegraphics[width=\textwidth]{average-salary-bar-chart.pdf}
  \end{frame}

  \begin{frame}{Findings: Certifications}
    \includegraphics[width=\textwidth]{certifications-bar-chart.pdf}
  \end{frame}

  \begin{frame}{Conclusion}
    \begin{itemize}
      \item compared multiple scraping tools
      \item developed a program for scraping data from three job search sites
      \item findings can be used to inform new decisions on what should be taught in universities
      \item more data points could be implemented in a future revision of this survey
      \item survey could be conducted again within a longer time span
      \item survey could be conducted again with additional job search websites
    \end{itemize}
  \end{frame}
\end{document}

>>>>

\institute{supervised by Irdin Pekaric}

@@

  \begin{frame}{Outline}
    \begin{itemize}
      \item Motivation
      \item Introduction
      \item Overview of the Project Workflow
      \item Evaluation of Scraping Tools
      \item Implementation
      \begin{itemize}
        \item Scraping
        \item Natural Language Processing
        \item Data Analysis
      \end{itemize}
      \item Findings
      \item Conclusion \& Future Work
    \end{itemize}
  \end{frame}

  \begin{frame}{Motivation}
    \begin{itemize}
      \item information security becoming an essential area of expertise
      \item same understanding of the required skills by both companies and prospective employees
      \item get an overview of the current situation and trends regarding the information security job landscape
    \end{itemize}
  \end{frame}

  \begin{frame}{Introduction}
    \begin{itemize}
      \item scraping of three popular job search websites: Monster, Indeed and StepStone
      \item cleaning of scraped data
      \item extraction of information from cleaned data
      \item analysis of extracted information
    \end{itemize}
  \end{frame}

  \begin{frame}{Overview of the Project Workflow}
    \includegraphics[height=\textheight]{project-workflow.dot.pdf}
  \end{frame}

@@

  \begin{frame}{Findings: Employment Type}
    \includegraphics[height=\textheight]{employment-type-bar-chart.pdf}
  \end{frame}

  \begin{frame}{Findings: Education Type}
    \includegraphics[height=\textheight]{education-bar-chart.pdf}
  \end{frame}

  \begin{frame}{Findings: Location}
    \includegraphics[height=\textheight]{location-bar-chart.pdf}
  \end{frame}

  \begin{frame}{Findings: Location per Capita}
    \includegraphics[height=\textheight]{location-per-capita-bar-chart.pdf}
  \end{frame}

  \begin{frame}{Findings: Average Salary}
    \includegraphics[height=\textheight]{average-salary-bar-chart.pdf}
  \end{frame}

  \begin{frame}{Findings: Certifications}
    \includegraphics[height=\textheight]{certifications-bar-chart.pdf}
  \end{frame}

  \begin{frame}{Conclusion \& Future Work}
    \begin{itemize}
      \item compared multiple scraping tools
      \item developed a program for scraping data from three job search sites
      \item more data points could be implemented in a future revision of this survey
      \item survey could be conducted again within a longer time span
      \item survey could be conducted again with additional job search websites
    \end{itemize}
  \end{frame}
\end{document}
